The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-04-08 paper/sections/conclusion.tex
update captions and figure descriptions

SEM itself has much room for improvement. 
First, while we focus on NURBS surfaces here, the only part of SEM that is NURBS specific is the shape matching operation.
We believe there is potential to allow mixed models (models which include polygonal meshes, particles, subdivision surfaces and NURBS)
by extending the range of shape matching operations used by the algorithm. The shape matching operation itself could be improved to be material-aware 
(to better handle heterogenous materials) or to be robust to noisy data (allowing direct simulation of scanned data). 
It is also interesting to consider the relationship between our error term and the orthogonality constraint proposed by~\citet{Zhang:CompDynamics:2020}. 
Their approach could be used to remove this parameter from SEM entirely.
Finally, in this paper we have focused on applying SEM to physics-based animation, and there is a significant amount of additional work needed to 
extend SEM reliably into engineering applications.

>>>>

SEM itself has much room for improvement. 
First, while we focus on NURBS surfaces here, the only part of SEM that is NURBS specific is the shape matching operation.
We believe there is potential to allow mixed models (models which include polygonal meshes, particles, subdivision surfaces and NURBS)
by extending the range of shape matching operations used by the algorithm. The shape matching operation itself could be improved to be material-aware 
(to better handle heterogenous materials) or to be robust to noisy data (allowing direct simulation of scanned data).
\revise{Additionally, more effort is required to ensure that the shape matching fit is optimal, which we do not provide guarantees for with our hierarchical shape matching approach. In future work we intend to explore using robust solvers or orthogonal bases for the fitting step.} \ty{more can be said here I suppose. I tried pinv() on the beam, which surprisingly worked, but it's just unpredictable since it should still fail on my very basic 2D box example. Haven't done much experimentation beyond this though, so I just write future work}
It is also interesting to consider the relationship between our error term and the orthogonality constraint proposed by~\citet{Zhang:CompDynamics:2020}. 
Their approach could be used to remove this parameter from SEM entirely.
Finally, in this paper we have focused on applying SEM to physics-based animation, and there is a significant amount of additional work needed to 
extend SEM reliably into engineering applications.

### 2021-04-08 paper/sections/results.tex
update captions and figure descriptions

%\begin{wrapfigure}{l}{0.5\columnwidth}
%    	\includegraphics{figures/deflection.pdf}
%	\caption{\revise{Te maximum beam deflection, as a percentage of the FEM beam's maximum deflection, is shown to converge to the FEM result as we add more parts along the beam.}}
%	  \label{fig:plot_beam_deflection}
%\end{wrapfigure}
\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/deflection_full.pdf}
	\caption{\revise{Te maximum beam deflection, as a percentage of the FEM beam's maximum deflection, is shown to converge to the FEM result as we add more parts along the beam.}}
  \label{fig:plot_beam_deflection}
\end{figure}

@@

\revise{We perform a basic scalability test shown in \reffig{scalability} by iteratively adding more degrees of freedom to a model and measuring average runtime of a simulation step, and report the ratio of number of nonzeros in the stiffness matrix. We begin with a unit cube composed of 6 parts and on each iteration we extend the cube, adding 4 more parts. The raycasting quadrature is updated on each
iteration so that a constant number of samples (45 in this case) lie in each cube. This experiment was performed using a AMD Ryzen 2600 with 16GB of RAM}

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/scalability.pdf}
  \caption{\revise{As a more extreme example of the shape-aware property of our algorithm, we simulate a falling octopus, and observe the 8 limbs moving independently.}}
  \label{fig:scalability}
\end{figure}

>>>>

%\begin{wrapfigure}{l}{0.5\columnwidth}
%    	\includegraphics{figures/deflection.pdf}
%	\caption{\revise{Te maximum beam deflection, as a percentage of the FEM beam's maximum deflection, is shown to converge to the FEM result as we add more parts along the beam.}}
%	  \label{fig:plot_beam_deflection}
%\end{wrapfigure}
\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/deflection_full.pdf}
	\caption{\revise{Te maximum beam deflection, as a percentage of the FEM beam's maximum deflection, is shown to converge to the FEM result as we subdivide the beam.\ty{currently a very blank figure, which I dont mind, but could consider adding inset beam pictures to give an idea of how this experiment works}}}
  \label{fig:plot_beam_deflection}
\end{figure}

@@

\revise{We perform a basic scalability test shown in \reffig{scalability} by iteratively adding more degrees of freedom to a model and measuring average runtime of a simulation step, and report the ratio of number of nonzeros in the stiffness matrix. We begin with a unit cube composed of 6 parts and on each iteration we extend the cube, adding 4 more parts. The raycasting quadrature is updated on each iteration so that a constant number of samples (45 in this case) lie in each cube. This represents a best case scenario in which sparsity is maximized as the number of degrees of freedom increases. As performance is tied to sparsity of the stiffness matrix, we see reasonable growth in the reported times, despite minimal effort on optimizing performance. This experiment was performed using a AMD Ryzen 2600 with 16GB of RAM}

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/scalability.pdf}
  \caption{\revise{Here we progressively add more degrees of freedom to a beam by iteratively inserting 4 part sections, extending the beam in the $x$-axis direction at each step. On the left we report the number of non-zeros as a percentage of the total number of elements in the stiffness matrix (nnz$\%$)}. The right plot shows the average runtime of a simulation step as the number of degrees of freedom increases.}
  \label{fig:scalability}
\end{figure}
